Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-02 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Final touches

---
title: "Identifying Heterogeneity in SAR Data with New Test Statistics"
author:
  - name: Alejandro C. Frery
    affil: 1,*
    orcid: 0000-0002-8002-5341
  - name: Janeth Alpala
    affil: 2 
    orcid: 0000-0002-0265-6236
  - name: Abraão D. C. Nascimento
    affil: 2
    orcid: 0000-0003-2673-219X
affiliation:
  - num: 1
    address: |
      School of Mathematics and Statistics, Victoria University of Wellington, Wellington 6140, New Zealand
#email: alejandro.frery@vuw.ac.nz
  - num: 2
    address: |
      Departamento de Estatística, Universidade Federal de Pernambuco, Recife 50670-901, PE, Brazil
#email: janeth.alpala@ufpe.br, abraao@de.ufpe.br

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento,A.D.C.
# firstnote to eighthnote
#firstnote: |
 # Current address: Updated affiliation
#secondnote: |
  #These authors contributed equally to this work.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. 
  Such areas are often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation (CV). 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  Finally, we show that our proposal, the entropy-based test, outperforms existing methods such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
#These maps identify different types of targets.
# We show that our proposal outperforms its competitors using simulated and SAR data.
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  The author J.A. would like to thank the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE) for their support. 
authorcontributions: |
  All authors (A.C.F., J.A, and A.D.C.N.) discussed the results and contributed to the research. All authors have read and agreed to the published version of the manuscript.

funding: |
  This research received no external funding.
institutionalreview: |
 Not applicable.
#informedconsent: |
  # Any research article describing a study involving humans should contain this 
  # statement. Please add ``Informed consent was obtained from all subjects 
  # involved in the study.'' OR ``Patient consent was waived due to REASON 
  # (please provide a detailed justification).'' OR ``Not applicable'' for 
  # studies not involving humans. You might also choose to exclude this statement 
  # if the study did not involve humans.

  # Written informed consent for publication must be obtained from participating 
  # patients who can be identified (including by the patients themselves). Please 
  # state ``Written informed consent has been obtained from the patient(s) to 
  # publish this paper'' if applicable.
dataavailability: |
  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 30 April 2024).
# abbreviations:
#   - short: MDPI
#     long: Multidisciplinary Digital Publishing Institute
#   - short: DOAJ
#     long: Directory of open access journals
#   - short: TLA
#     long: Three letter acronym
#   - short: LD 
#     long: linear dichroism

@@

bibliography: references.bib
#appendix: appendix.tex
#endnotes: false
output:
  rticles::mdpi_article:
    extra_dependencies: longtable
---

@@

library(fitdistrplus)
library(ggplot2)
library(reshape2)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD
#library(MASS)#
# model selection AIC and BIC

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

@@

source("../Code/R/MainFunctions/van_es_estimator.R")
source("../Code/R/MainFunctions/correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../Code/R/MainFunctions/ebrahimi_estimator.R")
#source("../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/vasicek_estimator.R")
source("../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
#source("../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

@@

```{r Simulated_data_gi0, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121 )

@@

#print(
 # kbl(
knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$.",
    format = "latex",
    booktabs = TRUE,
    align = "crllllllllllll",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table",  position="hbt", linesep = "") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "r")%>%
    kable_styling(latex_options = "scale_down")#%>%
   # kable_styling( full_width = T)
  #)
  #kable_styling(latex_options = c("scale_down"))

@@

<!-- ACF This is an important contribution. Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close. Therefore, their difference should be small. Explain why you need \widebar{Z} -->
<!-- JA Corrected -->

@@

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator

)

@@

save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")

@@

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results1_", L, ".Rdata"))
}

@@

print(combined_plot)

@@

#cat("\\setlength{\\tabcolsep}{1.0pt}\n")

@@

print(table_result_combined)

@@

# }

@@

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{4pt}\n")
load("./Data/type_I_results.Rdata")
type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})
type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
load("./Data/results_power.Rdata")
summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)
combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})
table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z})$ test statistic.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccccc",
  escape = FALSE,
  digits = 4,
  label = "table_size_power",
  centering = FALSE,
  #linesep = "",
  table.envir = "table", position="htb", linesep = "")%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)
print(table_combined_result)
```

@@

<!-- \textcolor{red}{% -->
<!-- ADCN: Caros, esse é o ponto mais delicado da excelente ideia desse paper em minha opinião. Não me oponho a colocarmos a lognormal como uma possibilidade, mas é preciso deixar claro que é uma possibilidade empírica. Uma alternativa empírica para uma solução do momento usando distribuições mais desenvolvidas na literatura e que sejam analiticamente tratáveis. Estou pensando corretamente? Se sim, por que não log-t-student, log-Laplace, power exponential, Log-hyperbolic,.... (e a lista segue). Sugiro talvez indicar (i) a dedução da distribuição assintótica das estatísticas em função de CV e MNAD dando com entrada G0I ($\mathcal{H}_1$) e a Gamma ($\mathcal{H}_0$) como trabalho futuro. Do que eu entendi, a suposição da normal assintótica para entropia vem de uma coleção de trabalhos teóricos. Já a LN, do que percebi, não. Coloquei um comentário em verde. Vejam se estão de acordo. -->
<!-- } -->

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma.Rdata")

@@

#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")

@@

# Guardar los resultados en un archivo .Rdata
save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")

@@

# Modificar el nombre de la última columna para que esté en dos líneas
#combined$`Inverse Gaussian` <- c("\\multirow{2}{*}{Inverse}", "Gaussian")

@@

```{r Simulated_AIC_BIC_gamma_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
R <- 15000
mu <- 1
L <- 5
sample.sizes <- c(25, 49, 81, 121)

# madmedian <- function(x){
#   mdn <- median(x)
#   MAD <- 1.4826 * median(abs(x - mdn))
#   MAD/mdn
# }

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma_MnADmedian.Rdata")

@@

# madmedian <- function(x){
#   mdn <- median(x)
#   MAD <- 1.4826 * median(abs(x - mdn))
#   return(MAD/mdn)
# }

MnADmedian <- function(x){
  mdn <- median(x)
  MnAD <- mean(abs(x - mdn))
  MnAD/mdn
}
results_AIC <- data.frame(Test = character(),
                          SampleSize = integer(),
                          Normal = numeric(),
                          Lognormal = numeric(),
                          Gamma = numeric(),
                          Weibull = numeric(),
                          InverseGaussian = numeric())

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_GI0_MnADmedian.Rdata")

@@

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
#B <- 5
alpha1 <- -3.0

@@

#   colors <- c("#999999", "#E69F00", "#56B4E9", "#009E80", "#009E72","#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#56B4E9", '#999999','#E69F00', "indianred3","#00AFBB", "#E7B800", "#FC4E07")

@@

```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom. (\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$. ',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Phantom1.png")
knitr::include_graphics("../Figures/PNG/Phantom_label/Phantom_labels.pdf")

@@

We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
<!-- ACF Did you check this nominal value? It is interesting to estimate and use the equivalent number of looks -->
<!-- ACF Provide the spatial resolution -->
<!-- JA, OK -->
The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$. (\\textbf{b}) Illinois-Region 1, with $L=36$. \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")

@@

In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

@@

```
```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2. (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and  (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b.png")
knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Illinois_crops_1024.png")
knitr::include_graphics("../Figures/PNG/mnad_005_Illinois_crops_1024.png")

>>>>

---
title: "Identifying Heterogeneity in SAR Data with New Test Statistics"
author:
  - name: Alejandro C. Frery
    affil: 1,*
    orcid: 0000-0002-8002-5341
  - name: Janeth Alpala
    affil: 2 
    orcid: 0000-0002-0265-6236
  - name: Abraão D. C. Nascimento
    affil: 2
    orcid: 0000-0003-2673-219X
affiliation:
  - num: 1
    address: |
      School of Mathematics and Statistics, Victoria University of Wellington, 6140 New Zealand
#email: alejandro.frery@vuw.ac.nz
  - num: 2
    address: |
      Departamento de Estatística, Universidade Federal de Pernambuco, Recife 50670-901, PE, Brazil
#email: janeth.alpala@ufpe.br, abraao@de.ufpe.br

# author citation list in chicago format
authorcitation: |
  Frery, A.C.; Alpala, J.; Nascimento, A.D.C.
correspondence: |
  alejandro.frery@vuw.ac.nz
# document options
journal: remotesensing
type: article
status: submit
# front matter
#simplesummary: |
  #A Simple summary goes here.
abstract: |
  This paper presents a statistical approach to identify the underlying roughness characteristics in synthetic aperture radar (SAR) intensity data. 
  The physical modeling of this kind of data allows to use the Gamma distribution in the presence of fully-developed speckle, i.e., when there are infinitely many independent backscatterers per resolution cell, and none dominates the return. 
  Such areas are often called "homogeneous" or  "textureless" regions. 
  The $\mathcal{G}_I^0$ distribution is also a widely accepted law for heterogeneous and extremely heterogeneous regions, i.e., areas in which the fully-developed speckle hypotheses do not hold. 
  We propose three test statistics to distinguish between homogeneous and inhomogeneous regions, i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with a known number of looks. 
  The first test statistic uses a bootstrapped non-parametric estimator of Shannon entropy, which provides a robust assessment in the face of uncertain distributional assumptions.
  The second test uses the classical coefficient of variation (CV). 
  The third test uses an alternative form of estimating the CV based on the ratio of the mean absolute deviation from the median to the median. 
  We apply our test statistic to create maps of \(p\) values for the homogeneity hypothesis.
  Finally, we show that our proposal, the entropy-based test, outperforms existing methods such as the classical CV and its alternative variant, in identifying heterogeneity when applied to both simulated and actual data.
#These maps identify different types of targets.
# We show that our proposal outperforms its competitors using simulated and SAR data.
keywords: |
  SAR; heterogeneity; entropy;  coefficient of variation; hypothesis tests
acknowledgement: |
  The author J.A. would like to thank the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE) for their support. 
authorcontributions: |
  All authors (A.C.F., J.A, and A.D.C.N.) discussed the results and contributed to the research. All authors have read and agreed to the published version of the manuscript.

funding: |
  This research received no external funding.
institutionalreview: |
 Not applicable.
dataavailability: |
  The Sentinel-1  images are made publicly available by European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (accessed on 24 April 2024).
conflictsofinterest: |
  The authors declare no conflict of interest.
supplementary: |
 This article was written in Rmarkdown and is fully reproducible. The code and data are accessible at
 \url{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics} (accessed on 30 April 2024).

@@

bibliography: references.bib

output:
  rticles::mdpi_article:
    extra_dependencies: longtable
---

@@

library(fitdistrplus)
library(ggplot2)
library(reshape2)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")
)

@@

source("../Code/R/MainFunctions/van_es_estimator.R")
source("../Code/R/MainFunctions/correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../Code/R/MainFunctions/vasicek_estimator.R")
source("../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")
```

@@

```{r Simulated_data_gi0, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121 )

@@

knitr::kable(
    reshaped_results,
    caption = "Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=5$.",
    format = "latex",
    booktabs = TRUE,
    align = "crllllllllllll",
    escape = FALSE, 
    digits = 2,  
    label = "table2",
    centering = FALSE,
    table.envir = "table",  position="hbt", linesep = "") %>%
    add_header_above(c(" ", " ", "Bias" = 6,  "MSE" = 6)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
    row_spec(0,  align = "r")%>%
    kable_styling(latex_options = "scale_down")
```

@@

@@

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
  "$\\widetilde{H}_{\\text{E}}$" = bootstrap_ebrahimi_estimator,
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
)

@@

save(all_TestStatistics, execution_times, file = "./Data/results_data_time2.Rdata")
```

@@

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results1_", L, ".Rdata"))
}
```

@@

print(combined_plot)
```

@@

@@

@@

print(combined_plot1)
```

@@

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{4pt}\n")
load("./Data/type_I_results.Rdata")
type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})
type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
load("./Data/results_power.Rdata")
summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)
combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})
table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z})$ test statistic.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccccc",
  escape = FALSE,
  digits = 4,
  label = "table_size_power",
  centering = FALSE,
  table.envir = "table", position="htb", linesep = "")%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)

print(table_combined_result)
```

@@

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma.Rdata")
```

@@

@@

# Guardar los resultados en un archivo .Rdata
save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC.Rdata")
```

@@

@@

```{r Simulated_AIC_BIC_gamma_MnADmedian, echo=FALSE, message=FALSE, warning=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 15000
mu <- 1
L <- 5
sample.sizes <- c(25, 49, 81, 121)

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_gamma_MnADmedian.Rdata")
```

@@

@@

save(results_AIC, results_BIC, file = "./Data/results_AIC_BIC_GI0_MnADmedian.Rdata")
```

@@

print(combined_plot1)
```

@@

sample.size <- c(49)
R <- 15000
mu <- 1
L <- 5
alpha1 <- -3.0

@@

@@

```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom. (\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$. ',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Phantom1.png")
knitr::include_graphics("../Figures/PNG/Phantom_label/Phantom_labels.pdf")
```

@@

We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of 10 m both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels  and they contain mountainous areas, agricultural regions, water bodies and  urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$. (\\textbf{b}) Illinois-Region 1, with $L=36$. \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")
```

@@

In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.

```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

@@

```{r Illinois_crops_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2. (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and  (\\textbf{c}) $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b.png")
knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Illinois_crops_1024.png")
knitr::include_graphics("../Figures/PNG/mnad_005_Illinois_crops_1024.png")
